\documentclass[12pt]{report}

\usepackage{helvet}
\usepackage[margin=1.25in]{geometry}

\begin{document}

\fontfamily{phv}\selectfont

\renewcommand{\familydefault}{\sfdefault}

\setlength{\parskip}{12pt}
\setlength{\parindent}{0pt}

%\setlength{\oddsidemargin}{1in}
%\setlength{\evensidemargin}{\oddsidemargin}
%\setlength{\topmargin}{0pt}
%\setlength{\textwidth}{6.5in}
%\setlength{\textheight}{11in}
%\setlength{\headheight}{0pt}
%\setlength{\headsep}{0pt}

%\fontsize{10}{12}\selectfont%

\pagestyle{empty}

\begin{center}
\textbf{Biographical Sketch}

\textbf{Jeffrey A. Wiegley, Ph.D.}
\end{center}

\textbf{Professional Preparation}

University of Southern California\hfill Ph.D., December 1998\\
State University of New York at Buffalo\hfill B.S., May 1991

\textbf{Professional Appointments}

\underline{California State University Northridge}\\
Professor, Department of Computer Science\hfill 2014 -- Present\\
Associate Professor, Department of Computer Science\hfill 2008 -- 2014\\
Assistant Professor, Department of Computer Science\hfill 2002 -- 2008\\
Director of Pioneering Technology Group\hfill 2010--2013

\underline{National Telemedia Corporation}\\
Network Systems Manager\hfill 1999 -- 2002

\underline{MarchFirst}\\
Systems Analyst/Administrator\hfill 1997 -- 1999

\textbf{Publications}

\emph{CSU Northridge ETD Workflow}, Fitzgerald,
Steve, Wiegley, Jeff, et al., United States Electronic Theses
and Dissertation Association (peer-reviewed, presentation based conference), Claremont, CA July 2013

\emph{GSP: Extending G-Code using JSP servlet technologies},
	Nagle, Sean, Wiegley, Jeffrey A. IEEE Automation Science and Engineering, 2008.

\emph{Development of Engaging Projects for Embedded Applications},
  Wiegley, Jeffrey A. ASEE, 2008.

\emph{Priority Approximation for Batching},
	Bein, Wolfgang W., Noga, John, Wiegley, Jeffrey A. HICSS, 2008.

\emph{Experiments with Balanced-Sample Binary Trees},
  Barnes, Michael G., Noga, John, Smith, Peter D., Wiegley,
  Jeffrey A. SIGCSE, 2005.

\emph{Sorting Convex Polygonal Parts Without Sensors on a Conveyor},
	Wiegley, Jeffrey A.  Ph.D. Thesis, University of Southern California. December 1998.

\emph{The Mercury Project: A Feasibility Study for Internet Robots},
  K. Goldberg, S. Gentner, C. Sutter, and J. Wiegley. IEEE Robotics and Automation Magazine, 1999.

\emph{A Complete Algorithm for Designing Passive Fences
  to Orient Parts}, K. Goldberg, J. Wiegley, M. Peshkin, and
  M. Brokowski.  Assembly Automation, August 1997.  Award recipient:
  ``Highly Commended''.
  K. Goldberg, J. Santarromana, G. Bekey, S. Gentner, R. Morris,
  C. Sutter and J. Wiegley. SPIE OE Reports, June 1996.

\emph{A Complete Algorithm for Designing Passive Fences
  to Orient Parts}, K. Goldberg, J. Wiegley, M. Peshkin, and
  M. Brokowski.  IEEE International Conference on Robotics and
  Automation, Minneapolis, MN. April 1996.

\emph{Beyond the Web: Manipulating the Physical World
  via the WWW}, K. Goldberg, M. Mascha, S. Gentner, J. Rossman,
  N. Rothenberg, C. Sutter and J. Wiegley.  Computer Networks and ISDN
  Systems Journal, 28(1), December 1995.

\emph{Desktop Teleoperation via the WWW},  K. Goldberg,
  M. Mascha, S. Gentner, N. Rothenberg, C. Sutter and J. Wiegley.
  1995 IEEE ICRA. 

\emph{Beyond the Web: Excavating the Real World via
  Mosaic},  K. Goldberg, M. Mascha, S. Gentner, J. Rossman,
  N. Rothenberg, C. Sutter and J. Wiegley.  The 2nd International
  World Wide Web Conference, Chicago, IL. Oct 1994.

\emph{A Pivoting Gripper for Feeding Industrial Parts},
  K. Goldberg, B. Carlisle, A. Rao and J. Wiegley.  ICRA, San Diego,
  CA. May 1994.

\emph{Computing a Statistical Distribution of Stable
  Poses for a Polyhedron}, K. Goldberg, J. Wiegley and A. Rao.  30th
  Annual Allerton Conference on Communications, Control and Computing,
  University of Illinois, September, 1992.

\end{document}
